### 2019-10-09 peer-review/review-response.Rmd

- Tables should not have any empty cells as design element or because information is not available ('NA' (subsequently defined as not available or not applicable) can be used for example).

*We feel that the table design we have used clearly imparts the information that it contains - part of this design is empty cells to space information. NA has not been used as information is not missing in the conventional sense - the results tables combine two different models with different confounders (hence not all fields contain data). Having this information in a single table allows for easier between model comparisons which we feel is essential to the presentation of our results. We have also included all results in csv form for readers who wish to use our results programmatically. We have clarified this in the data availability section. However, we are happy to alter the table design if we can preserve the clarity of the results presentation and welcome your suggestions.*

- For all Figure and Table titles, when possible, please indicate at the end of the title, the geographical area, period and total number of items covered by the illustration. E.g. Table 1: Summary of relevance and eligibility criteria for each cohort, United Kingdom, 2000-2010 (n = xxx individuals)

*We have added location and temporal information to all tables/figures. As this was a retrospective whole population based study we are not clear that sample sizes are useful in this instance (as they are the whole population meeting the cohort critiera which is age based). We are happy to add this if your feel this is meaningful.*

@@

*Thank you for this detailed and helpful review. We agree that the findings from this study should be relevant to the global TB community. We particularly appreciate your suggestions for improving the discussion of the approach used.*

The authors created 8 cohorts, each for a 5-year follow-up, using tuberculosis surveillance data for the numerator and Labor Force Survey data for the population denominator. These procedures are all clearly explained. As it gets substantially steeper and difficult to follow for the more general user's consumption is when the models are elaborated in the same paragraph. Perhaps it would help to split the elements of describing the basic epidemiology of incidence rates and ratios from the latter into two separate paragraphs, so that those unfamiliar with "negative binomial models", "penalised by model complexity", and the intricacies of Bayesian estimation with Markov Chain Monte Carlo, etc. This would clarify that here is a basic methodology, and here is a complex modeling description, the former for every epidemiologist, the latter only for the seasoned expert in statistical modeling using special techniques. I concur that it should and has to be there, but the more basic working techniques of calculation might be preferably "visually" separated from complex modeling techniques, notably when unexplained acronyms such as "GBM" are interspersed that do not help in easily following what the modeler actually did. Nor does it become that clear why exactly these models were chosen and not something else. The reader should probably have some inkling what the motivation for model selection is.

*We agree that it is important that all readers can easily follow the analysis. We have split the modelling section as you suggested into a non-technical overview and a more technical discussion of the approach. As per the editor comment we have carefully reviewed the use of abbreviations and added definitions where missing.*
